---
title: "Your Tutorial Title"
author: "Your Name"
output:
  learnr::tutorial:
    theme: cosmo   # Choose a Bootstrap theme
    highlight: tango  # Syntax highlighting theme
    css: styles.css  # Custom CSS file for additional styling
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

```{html}
<style>
/* General Body Styling */
body {
    font-family: 'Helvetica Neue', Arial, sans-serif;
    color: #333;
    background-color: #f8f9fa;
}

/* Headers */
h1, h2, h3, h4, h5, h6 {
    color: #2c3e50;
    font-weight: 700;
}

/* Links */
a {
    color: #007bff;
    text-decoration: none;
}
a:hover {
    text-decoration: underline;
}

/* Code blocks */
pre, code {
    background-color: #f5f5f5;
    border: 1px solid #e0e0e0;
    padding: 5px;
    border-radius: 4px;
    font-size: 0.9em;
}

/* Buttons */
.btn {
    background-color: #007bff;
    border-color: #007bff;
    color: #fff;
}
.btn:hover {
    background-color: #0056b3;
    border-color: #004085;
}

/* Quizzes and Exercises */
.learnr-exercise, .learnr-quiz {
    border: 1px solid #e0e0e0;
    padding: 15px;
    border-radius: 4px;
    background-color: #ffffff;
    box-shadow: 0 0 10px rgba(0, 0, 0, 0.1);
}

</style>

```

## Topic 1

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaluated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

